BLUP anaysis

### 2020-05-05 R/rrBLUP_analysis_D2F.Rmd
Abstract and Intro work

phe_pre2 <- phe_pre %>% 
  mutate(PLANT_ID = case_when(grepl("AP13", PLANT_ID) ~ "AP13",
                              TRUE ~ PLANT_ID)) %>%
  dplyr::select(SITE, PLOT_GL, PLANT_ID, TC_EOS_2018, GR1:GR50)

phe_post2 <- phe_post %>%
  mutate(PLANT_ID = case_when(grepl("AP13", PLANT_ID) ~ "AP13",
                              TRUE ~ PLANT_ID)) %>%
  separate(SITE_PHE, into = c("site", "PHE"), sep = c(5)) %>%
  dplyr::select(-site) %>%
  filter(PHE %in% c("GR50","FL1", "FL50", "BIOMASS", "TC_EOS", "HT_PAN_EOS", "EM1", "EM50")) %>%
   pivot_wider(names_from = "PHE", values_from = "MEAS") %>%
  group_by(PLANT_ID, SITE) %>% add_tally(name = "Per_site_count") %>%
  dplyr::select(SITE:PLANT_ID, Per_site_count, everything())

phe_all <- phe_post2 %>%
  left_join(phe_pre2, by = c("SITE", "PLOT_GL", "PLANT_ID"))
```

>>>>

phe_pre2 <- phe_pre %>% 
  mutate(PLANT_ID = case_when(grepl("AP13", PLANT_ID) ~ "AP13",
                              TRUE ~ PLANT_ID)) %>%
  dplyr::select(SITE, PLOT_GL, PLANT_ID, TC_EOS_2018, GR1:GR50, SRV)

phe_post2 <- phe_post %>%
  mutate(PLANT_ID = case_when(grepl("AP13", PLANT_ID) ~ "AP13",
                              TRUE ~ PLANT_ID)) %>%
  separate(SITE_PHE, into = c("site", "PHE"), sep = c(5)) %>%
  dplyr::select(-site) %>%
  filter(PHE %in% c("GR50","FL1", "FL50", "BIOMASS", "TC_EOS", "HT_PAN_EOS", "EM1", "EM50", "SRV")) %>%
   pivot_wider(names_from = "PHE", values_from = "MEAS") %>%
  group_by(PLANT_ID, SITE) %>% add_tally(name = "Per_site_count") %>%
  dplyr::select(SITE:PLANT_ID, Per_site_count, everything())

phe_all <- phe_post2 %>%
  left_join(phe_pre2, by = c("SITE", "PLOT_GL", "PLANT_ID"))

phe_all %>%
  dplyr::select(SITE:PLANT_ID, BIOMASS, SRV) %>%
  write_rds(., path = "~/Github/pvdiv-fitness-2019/data/All_phenotypes_fitness.rds")
```
